# Partnering with us

```{r}
#| label: sponsors
#| results: asis
#| echo: false
#| warning: false
#| message: false
source("../R/sponsors.R")

render_sponsors_by_level(
    "../data/sponsors.csv",
    heading = "h2"
)
```


## About partnering with EuroBioC2026

[Bioconductor](https://bioconductor.org){target="_blank"} is a non-profit
organisation that supports one of the most widely used data analysis ecosystems
in genomics. Software packages are contributed by more than 1,200 community developers
worldwide, totaling over 55 million downloads by
[about 1.5 million distinct IP addresses](https://www.bioconductor.org/packages/stats/bioc/index.html){target="_blank"}
last year. 

The next edition of the European Bioconductor Conference (EuroBioC) will be held
in Turku, Finland, at the [University of Turku](https://www.utu.fi/en){target="_blank"}
on 3-5 June 2026. We expect over 150 participants from the European and global
bioinformatics community, coming from academia and industry.
We are welcoming bioinformaticians, method developers, practitioners
incorporating Bioconductor into robust workflows, and researchers using these
tools for biological and biomedical discovery.

**Why partner with us?** Your brand will gain high **visibility**
among leading bioinformatics researchers, software developers and end-users,
positioning your company as a key contributor to open science and innovation.
You can **showcase your technologies**, engage with our highly skilled and
motivated community, and **recruit** top talents to your team.

**Your support will help us provide a high-quality in-person event,
and increase equity, diversity and inclusion at EuroBioC2026** by reducing
registration costs and funding scholarships for students and other academic
participants from lower income countries or with no other means of funding.

**Four levels of partnership are available.** 
Partners of all levels are invited to submit an abstract within the deadline,
which will be subject to review alongside submissions by attendees.
Selected abstracts will be given the opportunity to give a short talk or
present a poster that may highlight the scientific interests of the
organisation, research applications of their product(s), etc.

\usepackage{amssymb}

```{r echo=FALSE}
url <- "../data/partners.csv"
df <- read.csv(url, check.names = FALSE)
df[df == "X"] <- "$\\checkmark$"
library(kableExtra)
```

```{r results="asis", echo=FALSE}
kbl(df, row.names = FALSE, align = c("r", rep("c", ncol(df) - 1))) |>
    kable_material() |>
    column_spec(1, width = "65%") |>
    column_spec(2:5, width = "10%") |>
    row_spec(seq(1, nrow(df), 2), background = "ghostwhite") |>
    cat()
```

::: {.callout-tip appearance="simple"}

The listed sponsor levels are indicative. We’re always open to discussion and
happy to tailor sponsorships to better suit your company’s needs and budget.
If you’re interested in collaborating, just reach out. We’d be happy to discuss!

:::

Interested in partnering with EuroBioC2026? Please contact
[eurobioc@bioconductor.org](mailto:eurobioc@bioconductor.org).
